### 2013-02-11 mcmc.tex
notes to self
outline notes

@@

...What should you report as the inferred parameter value and
associated uncertainty (error bar)?  What is an upper limit?

>>>>

\section{What is a sampling?}

...What is a sampling, heurstically?..

...What is the expectation integral in the sampling approximation?  Why is that a good idea?..

...How is the sampling of the marginalized pdf trivially constructed from the full sampling?..

...Some guidance of where this comes back up below..

@@

...What should you report as the inferred parameter value and
associated uncertainty (error bar)?  What is an upper limit?  Do this
all for ONE DIMENSION.

...Now for multiple dimensions...return to the marginalization point
from above...
